---
title: "Customer Ratings Analysis"
author: "Nicole Chua"
date: "1/31/2022"
output: 
  pdf_document:
    keep_tex: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
load("my_data.RData")
library(ggpubr)
library(rstatix)
library(dplyr)
library(knitr)
library(gplots)
```  

\section{Introduction}  

Our primary objective is to compare and rank the four types of businesses (BBQ, Burgers, Pizza, Sandwiches) from unpaid customer ratings. A customer provides ratings from 1-5 for every type of business and each set of business ratings by a customer is designated an elite or non-elite status. It is also possible that a customer contributes ratings as both an elite and non-elite. We are also interested in whether elite customers give higher ratings than non-elite customers.  


```{r data summary, eval = FALSE}
str(xMT_data_tall)
dim(xMT_data_wide)
```


Using the tall/long version of data, there are 3 non-numeric fields, 1 numeric field and 262 observations.  

\section{Methods} 

Since each customer rates all food types but only some are designated both elite statuses, food types is a within factor and elite status is a between factor. Thus, we use a repeated measures one-way ANOVA to compare the means of ratings by food types and a separate one-way ANOVA for elite status to test the two following sets of hypotheses:  

Hypotheses for the effect of food type:  

*H~0~*:  There is no difference in mean customer rating for any food type.  

*H~a~*: There is a difference in mean customer rating by food type.  

Hypotheses for the effect of elite status:  

*H~0~*:  There is no difference in mean customer rating for any elite status.  

*H~a~*: There is a difference in mean customer rating by elite status.  

\section{Results}  

\subsection{Summary statistics}

We start by computing the mean customer ratings of the four food types split by elite vs non-elite status and for each elite status as well in Table 1. 
\newpage
```{r}
library(knitr)
mean_table1 <- tapply(xMT_data_tall$rating, list(xMT_data_tall$food_type, xMT_data_tall$elite), mean)
mean_table1 <- rbind(mean_table1, tapply(xMT_data_tall$rating, xMT_data_tall$elite, mean))
rownames(mean_table1)[5] <- "Elite"
mean_table1 |> kable()
```  

\begin{center}  
Table 1: Mean customer ratings by food types and elite status  
\end{center}  
On average, the customers rated the food types in the order of Sandwiches being the highest, followed by Burgers, Pizza and then BBQ with the lowest average rating. Elite customers have a higher average rating than non-elite customers by 0.242 points. 


```{r, eval = FALSE}
xMT_data_tall %>%
  group_by(food_type, elite) %>%
  identify_outliers(rating)
```


```{r, fig.dim=c(7,3)}
bxp1 <- ggboxplot(xMT_data_tall, x = "food_type", y = "rating", color = "elite", xlab = "food type")
bxp1
```  

\begin{center}  
Figure 1: Box plot of mean customer ratings by food type and elite status
\end{center}  

Figure 1 shows the distribution of customer ratings for each population of food types separated by elite status.  


\subsection{ANOVA models}  

```{r a1}
# rm 1-way ANOVA for food_type factor
a1 <- aov(rating ~ food_type + Error(ID), data = xMT_data_tall)
# summary(a1)
```


```{r a1 table}
anova_summary(a1) |> kable()
```  
\begin{center}  
Table 2: Repeated measures one-way ANOVA for food type factor  
\end{center}


```{r a2}
# 1-way ANOVA for elite factor
a2 <- aov(rating ~ elite, data = xMT_data_tall)
anova(a2) |> kable()
```  
\begin{center}  
Table 3: One-way ANOVA for elite status factor  
\end{center}
```{r, eval=FALSE}
# bonferroni post-hocs for food_type  

pairwise.t.test(x = xMT_data_tall$rating, 
                g = xMT_data_tall$food_type, 
                paired = TRUE, 
                p.adjust.method = 'bonferroni')
```
```{r, fig.dim=c(7,4)}
plotmeans(rating ~ food_type, 
          data = xMT_data_tall, 
          xlab = "food type")
```  
\begin{center}  
Figure 2: Plot of means and confidence intervals for food type ratings  
\end{center}

Table 2 shows the results of the repeated measures one-way ANOVA for food types. Differences among customer ratings for different food types are statistically significant (as indicated by the *) thus we reject the null hypothesis and conduct Bonferroni correction post-hocs for paired data. The results for pairwise comparisons of food types using paired t tests and Bonferroni correction is statistically significant for all comparisons. 

Table 3 shows the results of the one-way ANOVA for elite or non-elite status. Differences among average elite and non-elite customer ratings are significant so we reject the null hypothesis.

Figure 2 shows the mean customer rating for each food type. Sandwiches rank highest, followed by Burgers, Pizza and lastly, BBQ.

\section{Conclusion}  

The ranking of food types according to average customer ratings are as follows:  

(highest)Sandwiches > Burgers > Pizza > BBQ(lowest)  

From the repeated measures one-way ANOVA test as seen in Table 2 and Bonferroni correction test results, these differences in mean customer ratings for food types are statistically significant for all comparisons.  

As for elite and non-elite customers, yes a customer with Elite = TRUE gives, on average, a higher rating than a customer with Elite = FALSE. From the one-way ANOVA for elite and non-elite status conducted in Table 3, elite customer ratings are 0.242 points higher than non-elite customer ratings and this difference is statistically significant.  













